On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-29 docs/mvfits_paper/mvf.tex
Update introduction

It is therefore efficient to avoid convergence issues by using accurate models for $\sigma\LMlmn$, which can then be used directly to calculate $h\LM$ via \eqn{hlm}, and thereby the \gw{} polarizations via \eqn{hrd}.

@@

For consistency with the multipolar content of current ringdown models, here, we extend previous results to include the most significant multipoles with $\ell \leq 5$.

>>>>

It is therefore efficient to use accurate models for $\sigma\LMlmn$ which avoids convergence issues. These can then be used directly to calculate $h\LM$ via \eqn{hlm}, and thereby the \gw{} polarizations via \eqn{hrd}.

@@

For consistency with the multipolar content of current ringdown models, we extend previous results to include the most significant multipoles with $\ell \leq 5$.
